httpcode
========

```{r echo=FALSE}
library("knitr")
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL,
            x[lines],
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![cran checks](https://badges.cranchecks.info/worst/httpcode.svg)](https://cloud.r-project.org/web/checks/check_results_httpcode.html)
[![codecov](https://codecov.io/gh/sckott/httpcode/branch/master/graph/badge.svg)](https://codecov.io/gh/sckott/httpcode)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/httpcode)](https://github.com/metacran/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/httpcode)](https://cran.r-project.org/package=httpcode)

`httpcode` is a tiny R package to search for and show http code messages and description. It's a port of the Python httpcode (https://github.com/rspivak/httpcode) library.

`httpcode` has no dependencies.

Follows RFC 2616 (https://www.ietf.org/rfc/rfc2616.txt), and for additional codes 
following RFC 6585 (https://tools.ietf.org/html/rfc6585).

Structure of information for each status code:

* `status_code` - the status code
* `message` - very brief message explaining the code
* `explanation` - more verbose explanation, but still short
* `explanation_verbose` - the complete explanation

## Installation

Stable version

```{r eval=FALSE}
install.packages("httpcode")
```

Development version

```{r eval=FALSE}
install.packages("pak")
pak::pkg_install("sckott/httpcode")
```

```{r}
library("httpcode")
```

## Search by http code

```{r}
http_code(100)
```

```{r}
http_code(400)
```

```{r}
http_code(503)
```

```{r}
http_code(999)
```

## Get verbose status code description

```{r}
http_code(100, verbose = TRUE)
```

```{r}
http_code(400, verbose = TRUE)
```

# Fuzzy code search

```{r}
http_code('1xx')
```

```{r output.lines = 1:10}
http_code('3xx')
```

```{r}
http_code('30[12]')
```

```{r}
http_code('30[34]')
```

## Search by message

```{r output.lines = 1:10}
http_search("request")
```

```{r}
http_search("forbidden")
```

```{r}
http_search("too")
```

```{r}
http_search("birds")
```


## Bugs/features?

See [issues](https://github.com/sckott/httpcode/issues)

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct][coc]. By participating in this project you agree to abide by its terms.

[coc]: https://github.com/sckott/httpcode/blob/main/CODE_OF_CONDUCT.md
